A Linear Regression Model for Predicting MSDN Forums Votes

### 2018-11-01 forums/postScraping/msdn.forums.rmd
nore

```{r}
qqnorm(fit200$residuals)
qqline(fit200$residuals)
plot(fit200)
#influencePlot(fit1000)
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
qqnorm(fit1000$residuals)
qqline(fit1000$residuals)
plot(fit1000)
#influencePlot(fit1000)
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
qqnorm(fit2000$residuals)
qqline(fit2000$residuals)
plot(fit2000)
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
qqnorm(log(fitall$residuals))
qqline(log(fitall$residuals))
plot(fitall)
```

>>>>

```{r echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
qqnorm(fit200$residuals)
qqline(fit200$residuals)
plot(fit200)
#influencePlot(fit1000)
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
qqnorm(fit1000$residuals)
qqline(fit1000$residuals)
plot(fit1000)
#influencePlot(fit1000)
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
qqnorm(fit2000$residuals)
qqline(fit2000$residuals)
plot(fit2000)
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
qqnorm(log(fitall$residuals))
qqline(log(fitall$residuals))
plot(fitall)
```
